Untitled

### 2022-06-23 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021.Rmd
manuscript update

Figures S1 to S10

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=15, fig.width=12,fig.cap="\\textbf{Fig. S6.} Regression tree analyses. Comparison of the regression tree analyses between the full set of species and the subset of species with floral rewards for each plant species level metric. "}

########################################################################################################################################################
#SCRIPT TO CALCULATE THE REGRESSION TREE OF NECTAR AND PLOT IT
########################################################################################################################################################
#READ NETWORK VISITATION DATA (VISITS AGGREGATED PER PLANT SPECIES)

library(rpart.plot)
library(rpart)

v_df_all <- readRDS("Data/RData/log_visits_all_tree.rds")
nd_df_all <-  readRDS("Data/RData/normalized_degree_all_tree.rds")
d_df_all <- readRDS("Data/RData/specialization_all_tree.rds")

#run  regression trees of the 3 metrics
set.seed(1)
tree_1 <- rpart(Visits~., data=v_df_all, cp=0.0054559,minbucket=50)

set.seed(1)
tree_2 <- rpart(`Normalized degree`~., data=nd_df_all, cp=0.0084459,minbucket=50)

set.seed(1)
tree_3 <- rpart(Specialization~., data=d_df_all, cp=0.0072192 , minbucket=50) #10

#NECTAR AND POLEN DATA
v_df <- readRDS("Data/RData/log_visits_subset_nectar_pollen_tree.rds")
nd_df <-  readRDS("Data/RData/normalized_degree_subset_nectar_pollen_tree.rds")
d_df <- readRDS("Data/RData/specialization_subset_nectar_pollen_tree.rds")

#Set correct colnames for plotting
colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")

colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")

colnames(d_df) <- c("Specialization", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")

set.seed(2)
tree1 <- rpart(Visits~., data=v_df,  cp=0.009000,minbucket=50)

set.seed(2)
tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.005000,minbucket=50)

set.seed(2)
tree3 <- rpart(Specialization~., data=d_df, cp=0.0050000,minbucket=50)

par(mfrow=c(3,2))

rpart.plot(tree_1, box.palette="GnOr", main="A Interaction frequency for all species", cex.main=1.85,tweak = 1.10) 
rpart.plot(tree1, box.palette="GnOr", main="B Interaction frequency for subset with floral rewards", cex.main=1.85,tweak = 1.10)

rpart.plot(tree_2, box.palette="GnOr", main="C Normalized degree for all species", cex.main=1.85,tweak = 1.10)
rpart.plot(tree2, box.palette="GnOr", main="D Normalized degree for subset with floral rewards", cex.main=1.85,tweak = 1.10)

rpart.plot(tree_3, box.palette="GnOr", main="E Specialization for all species", cex.main=1.85,tweak = 1.10) 
rpart.plot(tree3, box.palette="GnOr", main="F Specialization for subset with floral rewards", cex.main=1.85,tweak = 1.10)

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Fig. S7.} Phylogenetically informed principal component analysis (pPCA) for all plant species with the first (flower number - flower size axis) and third (style length - pollinator dependence axis) principal component that explained most trait variation."}
setwd("~/R_Projects/Reproductive Traits")

@@

\newpage
\thispagestyle{empty}
```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=19, fig.width=13, fig.cap="\\textbf{Fig. S8.} Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species. Categories that differ significantly are denoted with a different letter."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap="\\textbf{Fig. S9.} Interaction (yes/no) and visitation rate of the main bee families on the main axes of trait variation. Fitted posterior estimates of the presence-absence of interaction (plots a, b and c) and visitation rate (plots e, f and g) of Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae across PC1, PC2 and PC3. For visualization purposes, the response variable of number of visits was log-transformed (Y-axis of lower panel)"}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig. S10.} Plant species level metrics across the three main axes of trait variation.", fig.pos= "h"}

>>>>

Figures S1 to S9

@@

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Fig. S6.} Phylogenetically informed principal component analysis (pPCA) for all plant species with the first (flower number - flower size axis) and third (style length - pollinator dependence axis) principal component that explained most trait variation."}
setwd("~/R_Projects/Reproductive Traits")

@@

\newpage
\thispagestyle{empty}

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=19, fig.width=13, fig.cap="\\textbf{Fig. S7.} Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species. Categories that differ significantly are denoted with a different letter."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap="\\textbf{Fig. S8.} Interaction (yes/no) and visitation rate of the main bee families on the main axes of trait variation. Fitted posterior estimates of the presence-absence of interaction (plots a, b and c) and visitation rate (plots e, f and g) of Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae across PC1, PC2 and PC3. For visualization purposes, the response variable of number of visits was log-transformed (Y-axis of lower panel)"}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig. S9.} Plant species level metrics across the three main axes of trait variation.", fig.pos= "h"}
